Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard

### 2015-04-06 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Cleanup Bib file and latex
Added Refs to Ch 4

\begin{table}
	\centering
\begin{tabular}{|c|c|c|c|c|}
	\hline Density & \multicolumn{2}{c|}{Thermal Conductivity} & \multicolumn{2}{c|}{Specific Heat}   \\
    \hline (kg/m$^3$) & Temperature ($^\circ$C) & (W/mK)  & Temperature ($^\circ$C)  & (kJ/kg $^\circ$C) \\
	\hline 737  & 24 & 0.13 & 93 & 0.28 \\
	\hline  & 205 & 0.12  & 205 & 0.30 \\
	\hline  & 316 & 0.11 & 316 & 0.32 \\
	\hline  & 425 & 0.12 & 425 & 0.34 \\
	\hline  & 538 & 0.12 &  &  \\
	\hline
\end{tabular}
\caption[Thermal properties for Marinite I]{Thermal properties for Marinite I, as reported by the manufacturer BNZ3~\cite{Marinite:1997}}
\label{tab:Marinite_Thermal_Properties}
\end{table}

@@

According to the United States Geological Survey, most gypsum in the United States is used to make wallboards for homes and other structures.  A typical home in the United States contains more than 7 metric tons of gypsum ref USGS website http://minerals.usgs.gov/minerals/pubs/commodity/gypsum/.  As defined by ASTM, gypsum wallboard is gypsum board designed for use on walls, ceilings, or partitions and that affords a surface suitable to receive decoration~\cite{ASTM_C1396}. The ASTM standard further describes gypsum wallboard as having a noncombustible core, surfaced with paper bonded to the core. By weight, wallboard is composed of more than 85~\% gypsum, less than 10~\% cellulose, less than 3~\% starch and approximately 1~\% of both crystalline silica and fibrous glass.  Chemically gypsum can be described as calcium sulfate dihydrate, (CaSO$_{4}$2H$_{2}$O) .  By weight pure gypsum is approximately 79~\% calcium sulfate and 21~\% chemically bound water ref Lawson 1977.

@@

After receipt of the gypsum wallboard panels, the panels were laid out on the floor of the NIST Large Fire Research Laboratory, finished paper side up and painted with a roller.  The first coat was a latex primer, http://buyat.ppg.com/rep\_pafpainttools\_files/Pghpaints/tdb/78200.pdf.  Once the primer dried a top coat of white latex paint was applied http://buyat.ppg.com/rep\_pafpainttools\_files/Olympic/tdb/78010.pdf.  After the panels dried, they were weighed. The average mass of paint on the finished surface of the gypsum wallboard was 0.33~kg. Then the paint thickness was estimated an ultra sonic XXXX cite - in office.  Over the course of the experiments, random painted panels where checked with the ultra sonic device. The thickness of the paint varied from 0.05~mm to 0.13~mm.  Some of the painted panels were then cut-up into samples for the bench-scale experiments.

>>>>

\begin{table}
	\centering
\begin{tabular}{|c|c|c|c|c|}
	\hline Density & \multicolumn{2}{c|}{Thermal Conductivity} & \multicolumn{2}{c|}{Specific Heat}   \\
    \hline (kg/m$^3$) & Temperature ($^\circ$C) & (W/mK)  & Temperature ($^\circ$C)  & (kJ/kg $^\circ$C) \\
	\hline 737  & 24 & 0.13 & 93 & 0.28 \\
	\hline  & 205 & 0.12  & 205 & 0.30 \\
	\hline  & 316 & 0.11 & 316 & 0.32 \\
	\hline  & 425 & 0.12 & 425 & 0.34 \\
	\hline  & 538 & 0.12 &  &  \\
	\hline
\end{tabular}
\caption[Thermal properties for Marinite I]{Thermal properties for Marinite I, as reported by the manufacturer BNZ~\cite{Marinite:1997}}
\label{tab:Marinite_Thermal_Properties}
\end{table}

@@

According to the United States Geological Survey, most gypsum in the United States is used to make wallboards for homes and other structures.  A typical home in the United States contains more than 7 metric tons of gypsum ~\cite{USGS:2015}.  As defined by ASTM, gypsum wallboard is gypsum board designed for use on walls, ceilings, or partitions and that affords a surface suitable to receive decoration~\cite{ASTM_C1396}. The ASTM standard further describes gypsum wallboard as having a noncombustible core, surfaced with paper bonded to the core. By weight, wallboard is composed of more than 85~\% gypsum, less than 10~\% cellulose, less than 3~\% starch and approximately 1~\% of both crystalline silica and fibrous glass~\cite{GA:2010}. Chemically gypsum can be described as calcium sulfate dihydrate, (CaSO$_{4}$2H$_{2}$O) .  By weight pure gypsum is approximately 79~\% calcium sulfate and 21~\% chemically bound water~\cite{Lawson:1977}.

@@

After receipt of the gypsum wallboard panels, the panels were laid out on the floor of the NIST Large Fire Research Laboratory, finished paper side up and painted with a roller.  The first coat was a latex primer, http://buyat.ppg.com/rep\_pafpainttools\_files/Pghpaints/tdb/78200.pdf.  Once the primer dried a top coat of white latex paint was applied http://buyat.ppg.com/rep\_pafpainttools\_files/Olympic/tdb/78010.pdf.  After the panels dried, they were weighed. The average mass of paint on the finished surface of the gypsum wallboard was 0.33~kg. Then the paint thickness was estimated an ultrasonic coating thickness gauge~\cite{defelsko}.  Over the course of the experiments, random painted panels where checked with the ultra sonic device. The thickness of the paint varied from 0.05~mm to 0.13~mm.  Some of the painted panels were then cut-up into samples for the bench-scale experiments.
